diffusion, websites with 1 pc

### 2023-02-16 src/s_la_per_firm.Rmd
per firm

@@

```{r}
df.country <- df %>% group_by(year) %>% 
  summarise(n = sum(n))

@@

ggsave(path.out)

  #scale_x_date(breaks = df.test$year) 
```

@@

path.out <- paste0(path, "/outputs/xmid_f.png")
ggsave(path.out)

@@

# plots
path.out <- paste0(path, "/outputs/lad_")

>>>>

## Firms

```{r}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

df <- df %>% left_join(firms) %>% 
  mutate(n_by_firm = (n*1000)/firms) %>% # '000 websites/firm
  #filter(!is.na(firms)) %>% 
  select(-n, -firms) %>% 
  rename(n = n_by_firm)

# df %>% filter(is.na(n_by_firm))
# sapply(df %>% left_join(firms), function(x) sum(is.na(x)))
```

@@

```{r}
df.country <- df %>% group_by(year) %>% 
  summarise(n = sum(n, na.rm = T))

@@

ggsave(path.out)
  #scale_x_date(breaks = df.test$year) 
```

@@

path.out <- paste0(path, "/outputs/per_firm/xmid_f.png")
ggsave(path.out)

@@

# plots
path.out <- paste0(path, "/outputs/per_firm/lad_")

### 2023-02-16 src/test_gambling.Rmd
per firm

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)

@@

@@

## spatial data

```{r}
# get OA for England and Wales
path.geo <- paste0(path, "/data/raw/Output_Areas__December_2011__Boundaries_EW_BGC.geojson")
oa.ew <- readOGR(path.geo)
# source: https://geoportal.statistics.gov.uk/

# spatial transformations
oa.ew <- spTransform(oa.ew, CRS("+init=epsg:4326"))

# keep in the data slot only the ONS Output Area id, renaming it as 'id'
oa.ew <- oa.ew[, c('OA11CD', 'Shape__Area')]
colnames(oa.ew@data) <- c('id', 'area')

# reassign the polygon IDs
oa.ew <- spChFIDs(oa.ew, as.character(oa.ew$id))

# check the CRS has changed correctly, and the data slot has shrink to only the ID
summary(oa.ew)

# # get OA for Scotland
# path.geo.sc <- paste0(path, "/data/raw/SG_DataZoneBdry_2011")
# oa.sc <- readOGR(dsn=path.geo.sc, layer = "SG_DataZone_Bdry_2011")
# # source: https://data.gov.uk/dataset/ab9f1f20-3b7f-4efa-9bd2-239acf63b540/data-zone-boundaries-2011
# 
# # spatial transformations
# oa.sc <- spTransform(oa.sc, CRS("+init=epsg:4326"))
# 
# # Scotland (follows same steps as EW, see notes above)
# oa.sc <- oa.sc[, 'DataZone']
# colnames(oa.sc@data) <- c('id')
# 
# # reassign the polygon IDs
# oa.sc <- spChFIDs(oa.sc, as.character(oa.sc$id))
# 
# # check the CRS has changed correctly, and the data slot has shrink to only the ID
# summary(oa.sc)

path.geo.sc <- paste0(path, "/data/raw/output-area-2011-mhw")
oa.sc <- readOGR(dsn=path.geo.sc, layer = "OutputArea2011_MHW")
# source: https://www.nrscotland.gov.uk/statistics-and-data/geography/our-products/census-datasets/2011-census/2011-boundaries

# spatial transformations
oa.sc <- spTransform(oa.sc, CRS("+init=epsg:4326"))

# Scotland (follows same steps as EW, see notes above)
oa.sc <- oa.sc[, c('code', 'SHAPE_1_Ar')]
colnames(oa.sc@data) <- c('id', 'area')

# reassign the polygon IDs
oa.sc <- spChFIDs(oa.sc, as.character(oa.sc$id))

# check the CRS has changed correctly, and the data slot has shrink to only the ID
summary(oa.sc)

# build oa for GB
oa.gb <- spRbind(oa.ew, oa.sc)
rm(oa.ew, oa.sc)

# oa.gb$geometry <- oa.gb$geometry %>%
#   s2::s2_rebuild() %>%
#   sf::st_as_sfc()

# get GB
path.gb <- "/hdd/internet_archive/archive/gis/Countries_December_2014_Full_Clipped_Boundaries_in_Great_Britain.shp"
gb <- readOGR(path.gb)
# spatial transformations
gb <- spTransform(gb, CRS("+init=epsg:4326"))

## lisa maps

```{r}

path.out <- paste0(path, "/outputs/lisa_level_pc", n, "_oa") # for unique PC
#path.out <- paste0(path, "/outputs/lisa_level_pc", m, "_oa")  # for multiple PC

morani <- data.frame()

#spatial weight matrix
sf_use_s2(FALSE)
nb <- poly2nb(oa.gb)
listw <- nb2listw(nb, style = "W", zero.policy = T)

for (t in 1996:2012){
test <- oa.gb
test@data <- test@data %>% left_join(df[df$year==t,], by = c("id"="oa11cd")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),           # 0 for NAs and the same for year
         year = ifelse(is.na(year), t, year))

#spatial weight matrix
#moved out of the loop

#Moran's I
globalMoran <- moran.test(test$n, listw, zero.policy = T, na.action = na.exclude)
a <- cbind(globalMoran$estimate[[1]],globalMoran$p.value, t[1])
morani <- rbind(a, morani)

#LISA
lmoran<- cbind(test@data, localmoran(test$n, listw,  adjust.x=TRUE, zero.policy = T, na.action = na.exclude))
#lmoran

# centers the local Moran's around the mean
lmoran$Ii <- lmoran$Ii - mean(lmoran$Ii, na.rm = TRUE) 
lmoran$lag.n<-  lag.listw(listw,lmoran$n, NAOK = TRUE)

# centers the variable of interest around its mean

lmoran$ns <- lmoran$n - mean(lmoran$n, na.rm = TRUE) 
lmoran$lag.n <- lmoran$lag.n - mean(lmoran$lag.n, na.rm = TRUE)

signif <- 0.05
#lmoran

lmoran <- lmoran%>% 
  mutate(quadrant= ifelse(ns>0 & lag.n > 0, 1, 0)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.n < 0, 2, quadrant)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.n > 0, 3, quadrant)) %>% 
  mutate(quadrant= ifelse(ns>0 & lag.n < 0, 4, quadrant)) %>%   
  #mutate(quadrant= ifelse(lmoran$`Pr(z > 0)` > signif, 0, quadrant)) #%>% 
  mutate(quadrant= ifelse(lmoran$`Pr(z != E(Ii))` > signif, 0, quadrant)) #%>%

#   mutate(quadrant2= ifelse(ANC_st>0 & lagANC_st > 0, 1, 0)) %>% 
# mutate(quadrant2= ifelse(ANC_st<0 & lagANC_st < 0, 2, quadrant2)) %>% 
#   mutate(quadrant2= ifelse(ANC_st<0 & lagANC_st > 0, 3, quadrant2)) %>% 
#  mutate(quadrant2= ifelse(ANC_st>0 & lagANC_st < 0, 4, quadrant2)) %>% 
#  mutate(quadrant2= ifelse(lmoran$LISA_PANC > signif, 0, quadrant2))

mun_merge_new<- merge(test, lmoran, by="id")

# R p value map
breaks = c(0, 1, 2, 3, 4, 5)

cities <- maps::world.cities %>% 
  filter(country.etc=="UK") %>% 
  arrange(pop) %>% tail(10) 
tif_sf <- st_as_sf(cities, coords = c("long", "lat"), crs = 4326)

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, OA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(gb, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}
```

Moran I

```{r}
path.out <- paste0(path, "/outputs/morani_oa.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  kable() #%>% 
  #write_csv(path.out)

## Gini

```{r}

# add OAs with 0s
df.with0s <- df %>% mutate(country = substring(oa11cd, 1, 1)) %>%
  filter(country != "L" & country != "M" & country != "N") %>%
  filter(!is.na(country)) %>%
  complete(year, oa11cd, fill = list(n = 0)) %>%
  filter(year!=1000,
         !is.na(oa11cd)) %>%
  dplyr::select(-country)

gini.df <- data.frame()

for (t in 1996:2012){
    a <- df.with0s %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}

path.out <- paste0(path, "/outputs/gini_oa.csv")
gini.df %>% write_csv(path.out)
```

## Getis-Ord

```{r}

t= 1998
local_g <- localG(OA.Census$Qualification, nb_lw)
local_g <- localG(df[df$year==t,]$n, listw)

local_g <- cbind(OA.Census, as.matrix(local_g))
names(local_g)[6] <- "gstat"

## Distances to cities and retail centres

First set up the destinations. Origins are all the OA.

Major cities from [source](https://www.citypopulation.de/en/uk/cities/).
Retail centres from [source](https://data.cdrc.ac.uk/dataset/retail-centre-boundaries)

```{r}
# oa centroids
# oa.gb.c <- (rgeos::gCentroid(oa.gb, byid=TRUE))@coords %>% as.data.frame()
# oa.gb.c$id <- row.names(oa.gb.c)  #as_tibble(rownames = NA) %>% 
#   mutate(id = row.names())
oa.gb.c <- gCentroid(oa.gb, byid=TRUE)@coords %>% 
  as.data.frame() %>% 
  add_rownames(var = "id")

# cities
city.names <- c("London, UK", 
"Birmingham, UK",
"Glasgow, UK",
"Liverpool, UK",
"Bristol, UK",
"Manchester, UK",
"Sheffield, UK",
"Leeds, UK",
"Edinburgh, UK",
"Leicester, UK")

cities <- geo(city.names, no_query = F, method = "arcgis")

# retail centres
geo.path <- paste0(path, "/data/raw/Retail_Boundaries_UK.gpkg")
retail <-readOGR(geo.path) 
#retail.major.cetres <- subset(retail, retail$Classification == "Major Town Centre") #%>% 
retail.major.cetres.help <- gCentroid(retail, byid=TRUE)@coords %>% 
  as.data.frame() %>% 
  add_rownames(var = "id") #%>%

retail.major.cetres <- retail.major.cetres.help %>% 
  st_as_sf(coords = c("x", "y"), crs = 27700) %>%
  st_transform(4326) %>%
  st_coordinates() %>%
  as_tibble() %>% 
  bind_cols(retail.major.cetres.help$id) %>% 
  rename(id = '...3') %>% 
  left_join(retail@data %>% mutate(id = rownames(retail@data)), by = 'id')
```

Distance to cities

```{r}
dist <- distm(cbind(oa.gb.c$x, oa.gb.c$y), cbind(cities$long, cities$lat), fun=distHaversine) 
dist <- round((dist/1000),2) %>% 
  as_tibble()

city.names <- city.names %>% stringr::str_remove(", UK")
names(dist) <- city.names

dist <- dist %>% bind_cols(oa.gb.c$id) %>% 
  rename(oa11cd = last_col()) %>% 
  relocate(oa11cd)

# dist$dist <- names(dist)[apply(dist[-1], MARGIN = 1, FUN = which.min)]
# dist$distMet <- apply(dist[,2:11], 1, min)

dist <- transform(dist, dist = do.call(pmin, dist[-1]))

# NOT USED AS IT SCREWS UP THE REGRESSIONS
# Complete panel, N = 3871903, 17 year * 227759 OA
# df <- df %>% bind_rows(dist %>% dplyr::select(oa11cd)) %>%
#   mutate(year = ifelse(is.na(year),1000, year),
#          country = substring(oa11cd, 1, 1)) %>%
#   filter(country != "L" & country != "M" & country != "N") %>%
#   filter(!is.na(country)) %>%
#   complete(year, oa11cd, fill = list(n = 0)) %>%
#   filter(year!=1000,
#          !is.na(oa11cd)) %>%
#   dplyr::select(-country)

# tests
# test$country <- substring(test$oa11cd, 1, 1)
# unique(test$country)
# length(unique(test$oa11cd))

# calculate area
oa.gb$area <- area(oa.gb) #/ 1000000

# Join with distance and area
df <- df %>% left_join(dist, by = c("oa11cd" = "oa11cd")) %>% 
  left_join(oa.gb@data, by = c("oa11cd" = "id")) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)
sapply(df, function(x) sum(is.na(x)))
```

Distance to retail centres

```{r}
dist.retail <- distm(cbind(oa.gb.c$x, oa.gb.c$y), cbind(retail.major.cetres$X, retail.major.cetres$Y), fun=distHaversine) 
dist.retail <- round((dist.retail/1000),2) %>% 
  as_tibble()

# retail.names <- retail.major.cetres$RC_Name
# names(dist.retail) <- retail.names

dist.retail <- dist.retail %>% bind_cols(oa.gb.c$id) %>% 
  rename(oa11cd = last_col()) %>% 
  relocate(oa11cd)

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% dplyr::select(oa11cd, dist.retail)

# Join with complete panel
df <- df %>% left_join(dist.retail, by = c("oa11cd" = "oa11cd"))

sapply(df, function(x) sum(is.na(x)))
```

Website density regressions to London

```{r}
dens.London <- data.frame()
out.model <- data.frame()

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(London), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.London <- rbind(r2, dens.London)

  out.model_ <- tidy(model, conf.int = TRUE) %>% 
    slice(2) %>% 
    mutate_if(is.numeric, round, 2)
  out.model <- rbind(out.model_, out.model)
}

names(dens.London)[1] <- "rsquared"

path.out <- paste0(path,"/outputs/rsq_dist_london_oa.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

out.model <- out.model %>% 
  mutate(year = 1996:2012)

path.out <- paste0(path,"/outputs/b_dist_london_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

r2.all <- dens.London %>% 
  rename(London = rsquared)
```

Website density regressions to the nearest city

```{r}
dens.distMet <- data.frame()
out.modelMet <- data.frame()

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(dist), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.distMet <- rbind(r2, dens.distMet)

  out.model_ <- tidy(model, conf.int = TRUE) %>% 
    slice(2) %>% 
    mutate_if(is.numeric, round, 2)
  out.modelMet <- rbind(out.model_, out.modelMet)
}

names(dens.distMet)[1] <- "rsquared"

path.out <- paste0(path,"/outputs/rsq_dist_city_oa.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

out.modelMet <- out.modelMet %>% 
  mutate(year = 1996:2012)

path.out <- paste0(path,"/outputs/b_dist_city_oa.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

r2.all <- r2.all %>% left_join(dens.distMet) %>% 
  rename(cities = rsquared)
```

Website density regressions to the nearest retail centre

```{r}
dens.dist.retail <- data.frame()
out.model.retail <- data.frame()

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(dist.retail+0.001), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.dist.retail <- rbind(r2, dens.dist.retail)

  out.model_ <- tidy(model, conf.int = TRUE) %>% 
    slice(2) %>% 
    mutate_if(is.numeric, round, 2)
  out.model.retail <- rbind(out.model_, out.model.retail)
}

names(dens.dist.retail)[1] <- "rsquared"

path.out <- paste0(path,"/outputs/rsq_dist_centre_oa.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

out.model.retail <- out.model.retail %>% 
  mutate(year = 1996:2012)

path.out <- paste0(path,"/outputs/b_dist_centre_oa.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

# library(pscl)
# m1 <- zeroinfl((n) ~ log(dist.retail+0.001),
#   data = df[df$year==t,], dist = "negbin", EM = TRUE)
# summary(m1)
# 
# df %>% filter(year == 1996) %>% 
#   group_by(group = cut(n, breaks = c(0, 1, 2, 10, 100, 1000, 10000), include.lowest = T, right = F)) %>%  #seq(0, max(n), 100))) %>%
#   summarise(n = sum(n))
```
All R^2 dataframe

```{r}
path.out <- paste0(path, "/outputs/r2_all_oa.csv")

r2.all <- dens.London %>% 
  rename(London = rsquared) %>% 
  left_join(dens.distMet) %>% 
  rename(cities = rsquared) %>% 
  left_join(dens.dist.retail) %>% 
  rename(retail = rsquared) %>% 
  relocate(year, .before = London) %>% 
  arrange(year)

write_csv(r2.all, path.out)
```

## The below are unfinished

Website density regressions to the nearest retail centre with spatial lag

```{r}
library(spatialreg)

model <- lagsarlm(log(density+0.1) ~ log(dist.retail+0.1), data = df[df$year==t,], 
                  listw, tol.solve = 1e-30, zero.policy = T)

dens.dist.retail <- data.frame()
for (t in 1996:2012){
  model <- lm(log(density) ~ log(dist.retail+0.1), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.dist.retail <- rbind(r2, dens.dist.retail)
}
names(dens.dist.retail)[1] <- "rsquared"
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared))

## HH clusters

```{r}
hh <- mun_merge_new@data %>% filter(quadrant==1) %>% 
  select(id, quadrant) %>% 
  left_join(df[df$year==2000,], by =c("id" = "oa11cd")) %>% 
  select(id, year, n, area, density, London, dist, dist.retail)

hh.London <- lm(log(density+0.001) ~ log(London), data = hh)
summary(hh.London)
hh.dist <- lm(log(density+0.001) ~ log(dist), data = hh)
summary(hh.dist)
hh.retail <- lm(log(density+0.001) ~ log(dist.retail+0.001), data = hh)
summary(hh.retail)

df9610 <- read_csv(data.path9610) %>% 
  filter(V1.domain == n,
         year == 1999) %>% 
  left_join(lookup, by = "pc", suffix =c("",""))

hh %>% left_join(df9610, by =c("id"="oa11cd"))

Spatial regression

```{r}
library(splm)
m <- spml(log(n)~lag(log(n)), data = df, listw = listw, lag = TRUE, spatial.error = "b", 
          model = "within", effect = "individual", method = "eigen", na.action = na.fail)

>>>>

library(tidyverse)
library(rprojroot)
library(urltools)

@@

all

```{r}
data.folder <- "/hdd/internet_archive/archive/data/"
data.path.all <- paste0(data.folder, "all.csv")
all <- read_csv(data.path.all)

g <- all %>% filter(year==2010) %>% 
  filter(grepl('gambl', url)) #

#g %>% filter(year==2010)

#all %>% filter(grepl("^www.", host))
```
## hyperlinks

zgrep "gambleaware" host-linkage.tsv.gz | sort > gambleaware.tsv

```{r}
links.path <- "/home/nw19521/Downloads/gambleaware.tsv"

l <- read_delim(links.path, delim = "|", col_names = F) %>% 
  separate(X3, c('j', 'links'), sep = "\t") %>% 
  rename(year = X1,
         i = X2)
```
gamble is obtained by:
zgrep "gamble" host-linkage.tsv.gz | sort > gamble.tsv

It contains the hyperlink between domains that include the word "gamble".
There are 47795 obs (`dim(l)`) and 46293 unique hyperlinks (`length(unique(l$ij))`).

**Key message** the links are not repeated over time, only 47795 - 46293 = 1202.
2004 is the link-farm problem. 2008-2010 the number of links drops.

After i do the i join, there 935378 obs and 35751 postcode NA.

```{r}
links.path <- "/home/nw19521/Downloads/gamble.tsv"

l <- read_delim(links.path, delim = "|", col_names = F) %>% 
  separate(X3, c('j', 'links'), sep = "\t") %>% 
  rename(year = X1,
         i = X2) %>% 
  mutate(year = as.double(year),
         ij = paste(i, "_", j))

length(unique(l$ij))

l %>% group_by(year) %>% 
  summarise(n=n())

l %>% filter(year == 2010)

In 2010 492,575 rows. 7,868 without NA -- that is both i and j are geolocated --
only 11 distinct ij

In 2002 28,729,384 rows.  28,257,752 without NA -- that is both i and j are geolocated --
only 39 distinct ij

```{r}
l.pc <- l %>% 
  filter(year == 2002) %>% 
  left_join(all, by = c("i" = "host", "year" = "year")) %>% 
  left_join(all, by = c("j" = "host", "year" = "year"))
```

```{r}
l.pc %>% drop_na() %>% distinct(ij)
```

```{r}
length(unique(l.pc$ij))
```

```{r}
sapply(l.pc, function(x) sum(is.na(x)))
```

```{r}
l %>% 
  #filter(year == 2010) %>% 
  mutate(i.host = host_extract(i))

host_extract(l$i)
domain(l$i)
```

@@
